First steps in synthetic algebraic geometry

### 2017-03-15 snippets/open-subfunctors.tex
Notion of open truth values

% negneg-stability
% definition of open truth values

>>>>

It's worthwhile to introduce the notion of an \emph{open truth value}. This
files our approach to synthetic algebraic geometry in the established and more
general framework of synthetic topology~\cite{XXX}:

\begin{defn}In the context of a specified local ring, as for instance~$\affl$
of the big Zariski topos of a scheme, a truth value~$U \subseteq 1$ is
\emph{open} if and only if there exists an ideal~$J \subseteq \affl$ such
that~$\affl/J$ is quasicoherent and such that~$U$ holds if and only if~$1 \in
J$. (Section~\ref{sect:basics-on-truth-values} contains generalities on truth
values.)\end{defn}

\begin{prop}Let~$X$ be a Zariski sheaf. A subfunctor~$U \hookrightarrow X$ is
open if and only if, from the internal point of view of~$\Zar(S)$, for
any~$x\?X$ the truth value of~``$x \in U$'' is an open truth value.\end{prop}
\begin{proof}Immediate from the definition and the characterization given in
Proposition~\ref{prop:characterization-open-subfunctor}.\end{proof}

\begin{prop}In~$\Zar(S)$, open truth values are~$\neg\neg$-stable: If~$U
\subseteq 1$ is an open truth value, and if~$U$ does \notnot hold, then~$U$
actually holds.\end{prop}

\begin{proof}Since~$U$ is an open truth value, there exists an ideal~$J
\subseteq \affl$ such that~$\affl/J$ is quasicoherent and such that~$U$ holds
if and only if~$1 \in J$. By assumption, the element~1 is \notnot an element
of~$J$; we want to verify that it's actually an element of~$J$.

Since~$\affl/J$ is quasicoherent, the canonical homomorphism
\[ \affl/J \longrightarrow XXX \]
XXX
\end{proof}
